% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chang Zhao}

\basicInfo{
  \email{zhaochang206@gmail.com}\textperiodcentered\ 
  \phone{(+86) 130-0382-8195}\textperiodcentered\ 
  \linkedin[Chang Zhao]{https://www.linkedin.com/in/chang-zhao-chaz/}\textperiodcentered\ 
  \github[ZCplayground]{https://github.com/ZCplayground}\textperiodcentered\ 
  \homepage[My cnblogs]{https://www.cnblogs.com/ZCplayground/}}

\section{Education}
\datedsubsection{\textbf{Fuzhou University (FZU)}, Fuzhou, China}{Sept. 2015 - Jun. 2020}
\begin{itemize}
  \item \textit{Bachelor of Engineer} in Computer Science (CS)
  \item GPA : 3.01 / 5 (81.05 / 100), Major GPA: 3.59 / 5 (85.69 / 100)
\end{itemize}

\section{Experience}
\datedsubsection{\textbf{Software Development Intern at Microsoft Beijing, Cloud+AI Group}}{Jun. 2019 - Sept. 2019}
\begin{itemize}
  \item Designed a command line program, Layer 7 Packet Tracer, to locate the IP address of a device that will filter packets at specific application layers.
  \item Investigated the Protractor, Jasmine, and Selenium tools. Built a framework for the end-to-end front-end testing of the Privacy Review Manager project. Completed 31 test cases with ~1k lines of code.
  \item Designed a more flexible, configurable, and more versatile front-end progress bar component.
\end{itemize}

\datedsubsection{\textbf{FZU-SDN Lab Member}}{Mar. 2017 - Nov. 2019}
\begin{itemize}
  \item As a member of the FZU-SDN Lab (Software-defined Network) under supervision of Prof. Dong Zhang. My research
  interests included Software-defined Network, network security, programmable data plane and packets processing
  optimization techniques (major in data plane development kit, DPDK).
\end{itemize}

\datedsubsection{\textbf{Teaching Assistant - C++ Object-oriented Programming Course}}{Feb. 2018 - Aug. 2018}
\begin{itemize}
  \item Arranged and graded for assignments, answered questions, guided students to learn, hosted regular meetings with students and professor.
\end{itemize}

\section{Publications}
\begin{itemize}
  \item Binjie He, Dong Zhang, \textbf{Chang Zhao} (2019). \href{https://academic.oup.com/comjnl/advance-article-abstract/doi/10.1093/comjnl/bxz142/5666159}{\textit{Hidden Markov Model-based Load Balancing in Data Center Networks}}, The
  Computer Journal.
  \item Danhong Zhu, Dong Zhang, Binjie He, \textbf{Chang Zhao}, Xiang Chen (2019). \href{https://ieeexplore.ieee.org/document/8845443}{\textit{Design and Implementation of an Experimental Teaching Scheme for the Development of SDN Northbound Applications}}, IEEE ICCSE.
\end{itemize}

\section{Honors and Awards}
\begin{itemize}
  \item National College Students Innovation and Entrepreneurship Project, ``Development \\of Network Stream Classification Based on DPDK'', excellent grade \hfill Jun. 2019
  \item Second-Class Prize of China Collegiate Computing Contest, Network Technology \\Challenge Competition \hfill Aug. 2018 
  \item Second-Class Prize of The 4th National University SDN Application Innovation \\Development Competition \hfill Aug. 2017
  \item The Second-Class Fuzhou University Scholarship \hfill Mar. 2017
  \item Third-Class Prize of 2016 National English Competition for College Students \hfill Oct. 2016
\end{itemize}

\section{Projects}
\datedsubsection{\href{https://github.com/jishiDevelopers/jishi-backend}{\textbf{Jishi App Project}}}{Sept. 2018 - Dec. 2019}
\begin{itemize}
  \item Software engineering course project in cooperation with 8 classmates.
  \item A canteen dishes recommendation app for FZU teachers and students, which contains all restaurants in FZU and includes around 1300 dishes. More than 200 users downloaded and used our APP.
  \item I led a team of 4 classmates, designed and developed the backend system.
\end{itemize}

\datedsubsection{\textbf{Optimization on Network Flow Classification based on Intel DPDK}}{Apr. 2018 - May. 2019}
\begin{itemize}
  \item Used DPDK to implement multi-queue QoS on NIC and optimize the flow classification procedure.
\end{itemize}

\datedsubsection{\href{https://github.com/ZCplayground/Understanding-Unix-Linux-Programming}{\textbf{Unix/Linux Commands Programming}}}{Apr. 2018 - May. 2018} 
\begin{itemize}
  \item Implemented a series of Unix/Linux commands, such as \textit{more, who, cp, ls, pwd}. This project also includes some advanced topics like socket programming, HTTP web server and implementing a Shell.
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:} experienced in C / C++ / C\#, comfortable with Python / Javascript / PHP.
  \item \textbf{Computer Network:} Famillar with TCP/IP stack, basic SDN concept and configuration, developing under Linux OS.
  \item \textbf{Front-end and Back-end devlelopment:} Angular, Laravel.
  \item \textbf{Languages ability:} English(Fluent. TOEFL:101, GRE:319), Mandarin(Native).
\end{itemize}

\section{Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item I am passionate about computer science knowledge and have a strong willingness to self-learning. I learned professional computer science textbooks like \textit{CSAPP, CLRS, TCP/IP Illustrated, Volume 1: The Protocols, APUE} by myself.
  \item I joined a \href{https://github.com/EugeneLiu/translationCSAPP/commit/b90a9547a259420e0c21fa4ca73ca1e1619deb63}{project} that makes captions for the \textit{Introduction to Computer Systems (ICS)} video lessons of CMU (Carnegie Mellon University). \href{https://www.bilibili.com/video/BV1iW411d7hd?p=11}{I made the Chinese subtitle translation for the class "Memory Hierarchy".}
  \item In my spare time, I like swimming, playing Japanese Mahjong and Texas Hold'em. I spend a lot of time on reading books, writing personal blogs and making friends.
  \item I am a big fan of classical music. I have heard many piano concertos and recitals of famous classical orchestra and pianists. I taught myself the piano and played Debussy's Clair de lune(Moonlight) on stage.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
